---
title: "Excercise - Download climate data"
subtitle: "Biologia della Conservazione 25/26"
author: "Giuliano Colosimo"
institute: "University of Rome Tor Vergata"
format: 
  beamer: 
    aspectratio: 32
    keep_tex: true
    navigation: empty
    mainfont: "Atkinson Hyperlegible"
    toc: false
    toc-title: "Table of contents"
    slide-level: 2
    urlcolor: olive 
    citecolor: red
    linkcolor: gray
    include-in-header:
      - text: |
          \usepackage{amsmath}
          \usepackage{tikz}
          \setbeamertemplate{footline}[page number]
          \addtobeamertemplate{headline}{}{%
            \begin{tikzpicture}[remember picture,overlay]
              \node[anchor=north east,yshift=-4pt] at (current page.north east) {
                \includegraphics[width=2cm]{../../figures/Tor-Vergata_logo_cmyk.png}
              };
            \end{tikzpicture}%
          }
editor: visual
bibliography: ../../comprehensive_database.bib
csl: ../../apa_5th_edition.csl
citation_package: natbib #biblatex
---

## On-line data resources

-   [Eurostat](https://ec.europa.eu/eurostat/web/main/data)

-   [NOAA](https://www.noaa.gov)

-   [NASA](https://data.nasa.gov/browse)

-   [Our World in Data (via GitHub)](https://github.com/owid/co2-data)

-   [Copernicus](https://cds.climate.copernicus.eu/cdsapp#!/search?type=dataset)

-   [Automated Surface Observing System (ASOS)](https://mesonet.agron.iastate.edu/ASOS/)

---

-   We will be downloading historical data from the ASOS data repository available at Iowa State.

-   We will working on data from the Italian network of automated weather stations.

-   First lets take a look at the website to see how we can use R to automate the process of downloading the data and eventually analyse them.

- [Automated Surface Observing System (ASOS)](https://mesonet.agron.iastate.edu/ASOS/)

## The packages we will be using

```{r echo=TRUE, eval=FALSE}
# Installing the appropriate libraries
install.packages(c("jsonlite", "RCurl", "lubridate",
                   "dplyr", "ggplot2"))
```

\vspace{.5cm}

```{r echo=TRUE, eval=TRUE}
# Load libraries in the working environment
library(jsonlite)
library(RCurl)
library(lubridate)
library(dplyr)
library(ggplot2)
```

## Input from the user

- Now that we know the web site, we can set up a script to automate data downloading

```{r echo=TRUE, eval=TRUE}
# first, we need to specify the date boundaries
# start date in year, month, day format
startDate <- ISOdate(1990, 1, 1) 
# end date in year, month, day format
endDate <- ISOdate(2020, 12, 31) 

# second, we need to specify the data network parameter 
# we want to download the data from
# and the state we want to download the data from
user.network <- c("ASOS")
user.state <- c("IT") #state
```

---

- We can now start and retrieve the identifier of all the weather stations we are interested in.

```{r echo=TRUE, eval=TRUE}
network <- paste(user.state, 
                 user.network, sep = "__")
uri <- 
  paste("https://mesonet.agron.iastate.edu/geojson/network/",
        network, ".geojson", sep="")
uri
```

---

- We use the URL address we have prepared and try to retrieve the information we want.

```{r echo=TRUE, eval=TRUE}
# first we tell R that that we work with an URL
# URL = Uniform Resource Locator
# in this way R will be opening a connection to that URL 
# and we will be able to access the website
data <- url(uri)
data
```

